### 2019-11-21 README.Rmd
add travis, dockerfile, binder

>>>>

<!-- badges: start -->
[![Travis-CI Build Status](https://travis-ci.org/parkgayoung/koreapaleolithicmobilityoccupation.svg?branch=master)](https://travis-ci.org/parkgayoung/koreapaleolithicmobilityoccupation)
[![Launch Rstudio Binder](http://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/parkgayoung/koreapaleolithicmobilityoccupation/master?urlpath=rstudio)
<!-- badges: end -->
